% !TEX root = ../../thesis.tex

\chapter{The Uber Basics of \LaTeX{}}%
\label{ch:basics}%
\graphicspath{{chapters/basics/figures/}}

This chapter will briefly expose you to the basics.
It is not a replacement for looking things up online, so make sure you do that too.
I particularly like \url{https://www.overleaf.com/learn} as it is quite digestible.
Make sure you're reading through the actual source files at the same time, as I have left practical comments explaining in more detail than you see here.

I recommend you start by opening \verb|thesis.tex| which is the main file of this template.
Take note of the \verb|\documentclass| command at the top which provides many options for how your document looks.
By default, this template is setup for one-sided A4 paper, 12pt font, a custom font, custom margins, a custom bibliography style, a specific type of heading on each page, and has draft mode turned on (which is why you see line numbers in the margins and a watermark in the footer).
I have included the configurations that I used for my online and print thesis submission variations.

% My personal structure is to have a 'main' file for each chapter, in this case `basics.tex', which then
% includes several other files, one for each section (we will get to structure later on).
% I recommend this method as once your thesis becomes large, having monolithic files can be difficult to manage.

% This is how you directly paste a file into another file.
% ! IMPORTANT NOTE !
% See how this is `input` rather than `include` in thesis.tex? There's an extremely important difference.
% Using `include` will ensure the included content starts on a NEW page. That is, if you're one line over a page and use `include`, it will skip the rest of that page entirely.
% Using `input` will treat it as if you just copy and pasted the file's contents here, not skipping anything.
\input{chapters/basics/structure}
\input{chapters/basics/formatting}
\input{chapters/basics/figurestables}
\input{chapters/basics/citing}
\input{chapters/basics/other}
