% !TEX root = ../../thesis.tex

\section{Citing \& Referencing}%
\label{sec:basics-citing_and_referencing}%

\subsection*{Citing External Works}%
When citing external works, you must firstly add an entry to a \verb|.bib| file.
This template includes \verb|mypubs.bib| for your own works and \verb|\references.bib| for other works.
Once you have added an entry to a \verb|.bib| file, you are ready to cite it in text.

By default, this template uses a custom bibliography style named \verb|ieeecustom| which derives from the original \verb|ieee| style.
The only modification is that it uses \textit{Sentence Case Like This} rather than \textit{Regular case like this}.
Feel free to change this in \verb|preamble.tex|.

\begin{table}[!htbp]
  \centering
  \caption{A list of the most common citation commands.}%
  \label{table:basics-citing_examples}
  
  \begin{tabular}{>{\raggedright\arraybackslash}p{0.55\linewidth} >{\raggedright\arraybackslash}p{0.35\linewidth}}
    \textbf{Command} & \textbf{Example}\\
    \toprule

    \verb+Example~\cite{green_useoftools_2021}+ & Example~\cite{green_useoftools_2021}\\
    \verb+\citeauthor*{green_useoftools_2021}+ & \citeauthor*{green_useoftools_2021}\\
    \verb+\citeauthor{green_useoftools_2021}+ & \citeauthor{green_useoftools_2021}\\
    \verb+\citeyear{green_useoftools_2021}+ & \citeyear{green_useoftools_2021}

    \end{tabular}
\end{table}

Table~\ref{table:basics-citing_examples} shows several of the most common citation commands and an example of each.
Take careful note of the \verb|~| symbol before \verb|\cite|.
This character is a \textit{non-breaking space} which means that the word before it, in the above case ``Example'', will not be separated from the text that follows, in the above case the \verb|\cite| command.
Practically, this means that you will never have a word and its citation separate from one another at a line break, for instance.
It is important to note that \verb|~| \textbf{replaces} a regular space between the two, but visually appears identical; only its behavior changes.

It is also possible insert a complete citation by using the \verb|\fullcite| command:

\medskip

\noindent\fullcite{green_useoftools_2021}


\subsection*{Citing Internal Elements}%
If you instead want to reference something \textbf{internal} to the document, such as a figure, table, or chapter and so on, then you will be using the \verb|\ref| command.

If you look back at the tables, figures, and section headings in the \LaTeX{} code so far, you'll see liberal use of the \verb|\label| command.
This is what creates an anchor that we can use \verb|\ref| to refer to.

I may want to raise something discussed in Chapter~\ref{ch:introduction}, or a specific section such as \S\ref{sec:basics-formatting}.
Tables and figures are exactly the same --- consider Table~\ref{table:basics-citing_examples} or Figure~\ref{fig:basics-skyrim_book}.

Again note the use of \verb|~| as a non-breaking space before \verb|\ref|.
The exception to this is when using the \verb|\S| command (\S), as that symbol typically does not have a space at all.
